---
title: "Assignment Web APIs"
author: "Samuel I Kigamba"
date: "October 27, 2019"
output:
  pdf_document:
    extra_dependencies:
    - geometry
    - multicol
    - multirow
    - xcolor
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis
You will need to start by signing up for an API key.

Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and
transform it into an R DataFrame.

Load all the relevant libraries (install packages if none exists)
```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(stringr)
library(httr)
library(jsonlite)
library(tidyr)
```

```{r, include=FALSE}
api_key <- "&api-key=wlu8Jq1oRhyXKrF9vK5dBY4OsAE3W9aO"
```

Define the HTTP request and in this case from the NYT website :
https://developer.nytimes.com/docs/articlesearch-product/1/routes/articlesearch.json/get
Follow the instructions in the link provided above to set an API key for use to access the required data
```{r}
HTTP_request <- "https://api.nytimes.com/svc/search/v2/articlesearch.json"
```

Define the search Query in this case to search for business articles
```{r}
search_query <- "?q=business"
```

Apply filters to limit the results to business and finance. The following values are allowed:
day_of_week, document_type, ingredients, news_desk, pub_month, pub_year, section_name, source, subsection_name, type_of_material

```{r}
filters <- "&fq=document_type(article)&fq=news_desk(business)&fq=type_of_material(business)&fq=keyword(finance)"
```

Define the start (01/01/2015) and end dates of today (10/27/2019)
```{r}
start_date <- "&begin_date=20150101"
end_date <- "&end_date=20191027"
```

Sort by relevance (other allowable parameters include: oldest and newest)
```{r}
sort_by <- "&sort=relevance"
```

Hide API key
Include your API key generated from the website into a separate line of code and set the include paramenter in the R code block to FALSE
```{r}
hidden_API_key <- api_key
```

```{r}
business_articles <- fromJSON(paste0(HTTP_request, search_query, filters, start_date, end_date, sort_by, hidden_API_key))
results <- business_articles$response$docs
```

Follow the link below to see all the possible parameters
https://developer.nytimes.com/docs/articlesearch-product/1/routes/articlesearch.json/get
```{r}
business_df <- data.frame('Date' = format(as.Date(results$pub_date), "%B %d, %Y"),
                      'news_desk' = results$news_desk,
                      #'Headline' = results$headline$main,
                      'source' = results$source,
                      'URL' = results$web_url
                      )
business_df
```